RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-06-17 manuscripts/manuscript.Rmd
fix more citations

These examples use data from the popular phylogenetics software `geiger` `r citep(citation("geiger"))`.

@@

At the heart of the NeXML standard is the ability to encode arbitrary
metadata in precisely specified, machine-readable formats that maintain
backwards compabitibilty with any existing NeXML parser. NeXML uses the
"Resource Description Framework in Annotations", or RDFa `r citep("http://www.w3.org/TR/xhtml-rdfa-primer")`,
as described in @Vos_2012.  These annotations can be used to add 
information to any particular element of the data, (a tree, node, edge,
or taxonomic unit; a character matrix or specific trait, or even another 
metadata annotation or the NeXML data file as a whole). `RNeXML` provides
a range of tools for accessing metadata embedded in a NeXML file.

@@

`r citet("Revell phytools 2011")` describes the `phytools` package for R, which includes
utilities for reading, manipulating, and writing `simmap` files in R.
In this example, we also show how to define `RNeXML` functions that 
map the R representation used by Revell (an extension of the `ape` class)
into the NeXML extension we have defined by using `RNeXML` functions.

>>>>

These examples use data from the popular phylogenetics software `geiger` `r citep(citation("geiger")[[4]])`.

@@

At the heart of the NeXML standard is the ability to encode arbitrary
metadata in precisely specified, machine-readable formats that maintain
backwards compabitibilty with any existing NeXML parser. NeXML uses the
"Resource Description Framework in Annotations", or RDFa,
as described in @Vos_2012.  These annotations can be used to add 
information to any particular element of the data, (a tree, node, edge,
or taxonomic unit; a character matrix or specific trait, or even another 
metadata annotation or the NeXML data file as a whole). `RNeXML` provides
a range of tools for accessing metadata embedded in a NeXML file.

@@

`r citet(citation("phytools"))` describes the `phytools` package for R, which includes
utilities for reading, manipulating, and writing `simmap` files in R.
In this example, we also show how to define `RNeXML` functions that 
map the R representation used by Revell (an extension of the `ape` class)
into the NeXML extension we have defined by using `RNeXML` functions.
